---
title: "ldaviewerDSI"
author: "Arthur Koehl"
date: "May 1, 2019"
output: rmarkdown::html_vignette
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = TRUE,
  comment = "#>"
)
```

# Quick Start

This page outlines an example use for the ldaviewerDSI package using a corpus of movie reviews. We will process those reviews from raw text all the way to the final visualization. 

To do so we will need tm, lda, and topic models. 

Load packages
```{r}
library(tm) # for dtm
library(lda) # to run the lda model
library(topicmodels) # for dtm2ldaformat
library(ldaviewerDSI) # to create the viewer
```


Read in the documents
```{r}
idir = system.file("extdata", "reviews", package="ldaviewerDSI")
fnames = list.files(idir, pattern="*.txt", full.names=FALSE)
head(fnames)
```

Create a document term matrix with the tm package. We will use a sample of 500 of the documents to make this demo run quicker.
```{r}
s = sample(1:length(fnames), 500)
fnames = fnames[s]
raw = lapply(paste(idir,fnames,sep="/"), readLines)
corpus = tm::Corpus(tm::VectorSource(raw))
corpus = tm_map(corpus, tm::removePunctuation) #remove punctuation
corpus = tm_map(corpus, tm::removeNumbers) #remove numbers
corpus = tm_map(corpus, tm::removeWords, tm::stopwords("english")) #remove stopwords
dtm = tm::DocumentTermMatrix(corpus) #create dtm
dtm = tm::removeSparseTerms(dtm,.995) #remove sparse terms
inspect(dtm)
```


Run the topic model using lda.collapsed.gibbs.sample from the lda package.
```{r}
lda_input = topicmodels::dtm2ldaformat(dtm)
model = lda::lda.collapsed.gibbs.sampler(documents = lda_input$documents, K=20, vocab=lda_input$vocab, num.iterations=1000, alpha=0.5, eta=0.1, burnin=50)
```

Compute doc topics and topic terms
```{r}
doc_topics = t(apply(model$document_sums + 0.5, 2, function(x) x/sum(x)))
topic_terms = t(apply(t(model$topics) + 0.1, 2, function(x) x/sum(x)))
dim(doc_topics)
dim(topic_terms)
```

Create the website
```{r, eval=FALSE}
create_viewer(doc_topics, topic_terms, lda_input$vocab, fnames, idir, "./site/", verbose=TRUE)
```

You should now be able to view the website by opening ./site/index.html in a browser.
If you want to see how to add the LDAvis visualization to the site checkout the "withLDAvis" vignette.
